Combining living and fossil taxa into phylogenies: the missing data issue

### 2014-07-29 Manuscript/TEM_draft.tex
Acknowledgements notes

\section{Acknowledgements}
% NC: Try and keep these short and to the point
Thanks to Trevor Hodkinson and Andrew Jackson %Also Gavin Thomas, Emmanuel Douzery and Frédéric Delsuc if not authors. %NC: Also members of MacroJC - %TG : also Adam Kev and Sive or that's putting to many people, thinking about it, they helped at least as much as Andrew (not mentioning Trevor but that's more political)?
for useful comments on our simulation protocol and Paddy Doyle for  assistance with the computer cluster. Simulations used the Lonsdale cluster maintained by the Trinity Centre for High Performance Computing and funded through grants from Science Foundation Ireland. % NC: Is this what you're supposed to cite for the cluster? Check. - TG: yep
This work was funded by a European Commission CORDIS Seventh Framework Programme (FP7) Marie Curie CIG grant (proposal number: 321696).

>>>>

\section{Acknowledgements}
% NC: Try and keep these short and to the point
Thanks to Frédéric Delsuc, Emmanuel Douzery, Trevor Hodkinson and Andrew Jackson and the members of the Macro Journal Club %Also Gavin Thomas if not authors - %TG : also Adam Kev and Sive or that's putting to many people, thinking about it, they helped at least as much as Andrew (not mentioning Trevor but that's more political)?
for useful comments on our simulation protocol. Thanks to Paddy Doyle, Graziano D'Innocenzo and Sean McGrath for assistance with the computer cluster. Simulations used the Lonsdale cluster maintained by the Trinity Centre for High Performance Computing and funded through grants from Science Foundation Ireland. % NC: Is this what you're supposed to cite for the cluster? Check. - TG: yep
This work was funded by a European Commission CORDIS Seventh Framework Programme (FP7) Marie Curie CIG grant (proposal number: 321696).
